\documentclass[11pt]{letter}
\usepackage[margin=0.9in]{geometry}

\begin{document}

\begin{letter}{Hiring Committee \\
Servier U.S. \\
Boston, MA}

\date{\today}

\opening{Dear Hiring Committee,}

I am writing to apply for the Global Biometrics Intern position at
Servier. I am a PhD student in Statistics at the University of
Connecticut (passed the PhD Qualifying Exam) with research experience
in survival analysis, interim analysis, large-scale data analysis,
and reproducible statistical software development in R and Python.


My background aligns well with the role’s focus on clinical-trial
methodology and implementation. In an academia--industry collaboration
with Servier, I coauthored a manuscript in preparation for journal
submission on predictive-modeling--assisted interim analysis for
censored time-to-event trials. I developed an event-time prediction
framework for two-arm randomized trials with censoring and baseline
covariates, and assessed its impact on treatment-effect estimation,
conditional power, and interim futility decisions. I also proposed
evaluation metrics that quantify both conditional power forecast
accuracy and the quality of interim decisions in practical settings.


I also have strong experience in statistical computing and R package
development. I developed the R package \emph{subsampling}, a toolkit
for efficient large-scale modeling that computes optimal subsampling
probabilities to select informative subsamples while preserving
statistical efficiency. The package supports GLMs, multinomial
logistic regression, quantile regression, and rare event/rare feature
regimes, with complete documentation and vignettes. In particular, I
developed theory and practical methods for rare binary feature
modeling, including balanced subsampling approaches that ensure
adequate rare-feature representation without pilot sampling. This
experience maps directly to Servier’s needs for implementing
algorithms, building workflows, and documenting methods for use by
other researchers.


More broadly, I have a track record of cross-disciplinary
collaboration and translating technical ideas into clear, reproducible
deliverables. I am comfortable working independently under mentorship
and communicating results to both technical and non-technical
audiences. I am legally authorized to work in the United States and
would welcome the opportunity to contribute to Servier’s biometrics
team.

Thank you for your consideration. I would be glad to discuss my fit
for the role.





\closing{Sincerely,}
\vspace{-3.0\baselineskip}

Qingkai Dong \\
PhD Student in Statistics \\
University of Connecticut

\end{letter}

\end{document}
