
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}

% heading
\newcommand{\resheading}[1]{
  \vspace{8pt}
  \noindent\textbf{\large #1}
  \vspace{4pt}
  \hrule
  \vspace{8pt}
}

\begin{document}

% =======================
% Contact Information
% =======================
\begin{center}
    {\LARGE Qingkai Dong} \\
    \vspace{5pt}
    \begin{tabular}{ll}
      Email: \href{mailto:qingkai.dong@uconn.edu}{qingkai.dong@uconn.edu} &  Google Scholar: \href{https://scholar.google.com/citations?user=mojHlF4AAAAJ&hl=en&oi=ao}{Qingkai Dong} \\  GitHub: \href{https://github.com/dqksnow}{dqksnow} 
      &   Website: \href{https://dqksnow.github.io/}{dqksnow.github.io} \\
    \end{tabular}
  \end{center}
  
% =======================
% Education
% =======================
\resheading{Education}
\begin{itemize}[left=0pt, label={}]
    \item \textbf{PhD in Statistics} \hfill 2023 -- Expected 2027 \\
    University of Connecticut, Storrs, CT \\
    Advisors: \href{https://ossifragus.github.io/}{Prof. HaiYing Wang}  and \href{https://statcomp.org/?}{Prof. Jun Yan} 
    
    \item \textbf{MS in Mathematical Statistics} \hfill 2023 \\
    Zhongnan University of Economics and Law, Wuhan, China \\
    Relevant Coursework: Advanced Probability, Survival Analysis, Non-parametric Statistics \\
    Thesis: Variable Selection and Model Averaging Methods for Accelerated Failure Time Models \\
    Advisor: \href{https://hzhaozuel.github.io/}{Prof. Hui Zhao}
    
    \item \textbf{BS in Applied Statistics} \hfill 2020 \\
    Qingdao University, Qingdao, China \\
    Relevant Coursework: Real Analysis, Numerical
    Optimization, Linear Regression, Matlab, C++ \\
    Thesis: Automatic Marking System Based on Convolutional Neural Networks \\
\end{itemize}

% =======================
% Publication Experience
% =======================
\resheading{Publications}
\begin{itemize}[left=0pt, label={}]
\item \textbf{Dong Q}, Liu B, Zhao H. Weighted Least Squares Model Averaging for Accelerated Failure Time Models,  \emph{Computational Statistics and Data Analysis}, 2023, 184: 107743. \href{https://dqksnow.github.io/pdfs/dong2023weighted.pdf}{Pdf}
  
\item Zhao H, Liu B, \textbf{Dong Q}, The Jackknife Model Averaging of Accelerated Failure Time Model with Current Status Data, \emph{Acta Mathematicae Applicatae Sinica}, 2023, 46(3): 313-328. \href{https://dqksnow.github.io/pdfs/zhao2023jackknife.pdf}{Pdf}
  
\item Zhao H, \textbf{Dong Q}, A Variable Selection Method for the Additive Hazards Model with Current Status Data, \emph{Journal of Systems Science and Mathematical Sciences}, 2022, 42(5): 1314-1329. \href{https://dqksnow.github.io/pdfs/hui2022variable.pdf}{Pdf}
  
\end{itemize}


% =======================
% Publication Experience
% =======================
\resheading{Software}
\begin{itemize}[left=0pt, label={}]
\item \textbf{R package
\href{https://cran.r-project.org/web/packages/subsampling/index.html}{subsampling}}:
Drawing representative subsamples from massive dataset based on
tailored sampling probabilities. These probabilities are optimized for
specific goals, such as minimizing the variance of coefficient
estimates or reducing prediction error. It provides subsampling
strategies for common statistical models, including GLMs, quantile
regression and rare binary response modeling.
\end{itemize}



% =======================
% Experience
% =======================
\resheading{Experience}
\begin{itemize}[left=0pt, label={}]
  
    \item \textbf{Research Assistant}, University of Connecticut \hfill Aug 2023 -- Present \\
    Developed an R package
\href{https://cran.r-project.org/web/packages/subsampling/index.html}{subsampling}
which provides optimal subsampling methods for various statistical
models. Developed balanced subsampling methods that improve estimation stability and efficiency in the presence of rare binary features.

    \item \textbf{Research Assistant}, University of Connecticut and
Servier Pharmaceuticals \hfill Mar 2024 -- Dec 2025 \\
    A project on the application of machine learning methods in adaptive
clinical trial design. It includes the development of models for predicting
survival times of censored individuals and their application to improve the
accuracy of conditional power estimates and decision-making for interim analyses.

   \item \textbf{Research Project}, University of Connecticut \hfill Mar 2024 -- May 2024 \\
Applied statistical and clustering methods to analyze fluorescence
responses of porphyrinoid sensors to nitroaromatic compounds,
optimizing sensor selection for the detection and differentiation of
explosives.
      
    \item \textbf{Research Assistant}, University of Connecticut \hfill Jul 2024 -- Aug 2024 \\
    A project about the impact of social determinants of health (SDOH) and
frailty index on accelerated aging in breast cancer patients. It includes
pre-processing the data and performing statistical analyses on the All of Us
platform.
    
    \item \textbf{Teaching Assistant}, Zhongnan University of Economics and Law \hfill Sep 2020 -- Jan 2021 \\
    Assisted in the undergraduate course Probability Theory for 60+ students,
graded homework and exams.
  \end{itemize}


\resheading{Academic Presentations}
\begin{itemize}[left=0pt, label={}, itemsep=-8pt]
   \item Poster Presentation - New England Rare Disease Statistics (NERDS) Workshop, Boston, MA  \hfill Oct 2025 \\
   \item Poster Presentation - Dahshu Data Science Symposium, Storrs, CT \hfill Oct 2025 \\
\end{itemize}

\resheading{Academic Service}
\begin{itemize}[left=0pt, label={}, itemsep=-8pt]
   \item \textbf{Reviewer:} \textit{Statistical Papers}; \textit{Sankhya B}; \textit{Journal of Systems Science and Mathematical Sciences (Chinese)} \\
\end{itemize}

  
% =======================
% Awards
% =======================
\resheading{Awards}
\begin{itemize}[left=0pt, label={}, itemsep=-8pt]
   \item Predoc Fellowship at University of Connecticut \hfill 2025 \\ 
   \item First-class Scholarship at Zhongnan University of Economics and Law \hfill 2020, 2022 \\
   \item Second-class Scholarship at Qingdao University \hfill 2019  \\
   \item First Prize in China Contemporary Undergraduate Mathematical Contest in Modeling \hfill 2018  \\
   \item First Prize in China Electrical Math Modeling Competition \hfill 2018  \\
\end{itemize}

\end{document}
